Open Science, Open Plant Pathology

### 2020-07-24 analysis/paper/paper.Rmd
Cleanup Rmd file

Bayesian mixed effect models were fit using the contributed package brms [@Burkner2018] in the R environment  [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

@@

Model finesses were evaluated using model summaries and diagnostic plots from brms [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package bayesplot [@Gabry2019].

Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package bayestestR [@Makowski2019].

@@

No journals were completely closed, all offered at least an option for open access but some were completely open.

@@

Most articles did not make any computational methods available in any fashion with two classing as "3" (0.007&nbsp;%), which was the highest score available, 287 were classed as "0" (96&nbsp;%) and 9 articles (0.03&nbsp;%) appeared to not use any computational methods.

@@

The most frequently cited software was SAS.
The remainder were mostly specialised softwares with the exception of Microsoft Excel, tied for 9th.

@@

```{r software_used, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyr)

@@

```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An open and reproducible research workflow.', cache=FALSE, fig.env='figure'}
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

>>>>

Bayesian mixed effect models were fit using the contributed package 'brms' [@Burkner2018] in the R environment  [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

@@

Model finesses were evaluated using model summaries and diagnostic plots from 'brms' [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' [@Gabry2019].

Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' [@Makowski2019].

@@

No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.

@@

Most articles did not make any computational methods available in any fashion with two, 0.007&nbsp;%, classing as "3", which was the highest score available.
Two hundred eighty seven, 96&nbsp;%, were classed as "0" and 9 articles, 0.03&nbsp;%, appeared to not use any computational methods.

@@

The most frequently cited software was SAS.
The remainder were mostly specialised software with the exception of Microsoft Excel, tied for 9th (Table \@ref(tab:su)).

@@

```{r software_used, echo=FALSE, message=FALSE, warning=FALSE}
library("tidyr")

@@

```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An open and reproducible research workflow.', cache=FALSE, fig.env='figure'}
library("DiagrammeR")
library("DiagrammeRsvg")
library("rsvg")
